\section{introduction}

Active galactic nucleii are thought to be powered through the
accretion of matter from the proximal environment into a supermassive
black hole.  The radiation emitted excites the surrounding medium
which becomes detectable as narrow line regions, broad line regions
and optical continuum.  Moreover, in the direction perpendicular to
the accretion disk, where the medium is more transparent, jets will
appear.  If a jet is oriented towards the Earth, a quasar is observed
\citep[e.g.,][]{1984RvMP...56..255B}.  While the basic mechanism
\citep[originating in the work
  of][]{1964ApJ...140..796S,1964SPhD....9..246Z,1969Natur.223..690L}
is not in doubt, the central engines, near the event horizons of the
black holes, remain to be probed.

For the black holes in the Galactic centre and the centre of M87
---the two nearest objects that barely qualify as AGN--- the central
engines (which are $<0.1\rm\,mas$ on the sky) are close to being
resolved through very long baseline interferometry, which shows
preliminary indications of the jet-launching structures
\citep{2008JPhCS.131a2055D,2012Sci...338..355D,2013MNRAS.434..765K,2016arXiv160205527F}.
Current data do not deliver images, but require fitting to to
predefined models for the images.  A whole range of models have been
applied, starting from simple geometric models to more complex
physical models
\citep{2008Natur.455...78D,2011ApJ...738...38B,2009ApJ...706..497M,2010ApJ...717.1092D}.
The more complicated models nonetheless tend to predict a crescent
shaped silhouette of the black hole.  This motivated
\cite{2013MNRAS.434..765K} to use a simple geometric crescent model to
fit the data, and argued that the crescent is nothing but the
silhouette of the event horizon.

The great majority of quasars, however, lie at redshifts beyond 2
\citep{2014A&A...563A..54P} and their central engines would be orders
of magnitude smaller on the sky. The direct observations of the black
hole silhouettes of quasars is far beyond foreseeable instrumentation.
In the present paper we consider a possible indirect method,
previously investigated by \cite{1999ApJ...524...49A}, through which
gravitational microlensing could probe the black hole shadow and its
proximal quasar environment.

Gravitational microlensing of quasars, reviewed in
Section~\ref{sec:microlensing} below, refers to sharp changes in the
observed brightness of quasars that have been lensed by intervening
galaxies, without any changes in the intrinsic luminosity.
Microlensing affects only the light from the innermost part of the
quasar, such as the optical continuum
\citep[e.g.,][]{2012A&A...544A..62S} and is a consequence of two
things: the very small size of the central engine, and granularity of
the mass distribution of a lensing galaxy due to stars.  The latter
means that lensed brightness is not a smooth function of source
position, but a complicated network of singular curves known as
caustics.  Most astrophysical sources straddle several caustics, and
hence their net brightness varies smoothly with location.  The central
engine of quasars, however, is smaller.  Hence the lensed brightness
undergoes sudden changes as a quasar crosses a caustic.
Figure~\ref{fig:magnification_map} is a simple illustration.  The
effect supplies an upper limit on the size of the central engine, and
can also be used to study the mass distribution and kinematics of
stars in the lensing galaxy as well
\citep[e.g.,][]{2012ApJ...744..111P}.  Caustics have an additional
remarkable feature: though they can be very complicated, they have
some universal properties well-known from catastrophe theory.  In
particular, very close to the simplest caustics (known as folds), the
observed brightness is simple $\propto1/\sqrt p$ where $p$ is the
transverse distance of the source from the caustic.  Since the
observed brightness is a convolution of the magnification map with the
source brightness, the lightcurve provides tomographic information
about the source profile if the magnification map is known.
\cite{1999ApJ...524...49A} showed that if the latter is the
magnification near a pure fold, the brightness distribution of the
source can in principle be deconvolved out of the light curve.
Applied by \cite{2012MNRAS.423..676A} Pure folds, however, are not to
be found in real systems.  In this paper we argue a simpler form of
the idea holds more promise.  We show that if a quasar crosses not a
pure but still fairly clean fold, such as in
Figure~\ref{fig:magnification_map}, the simple crescent model of
\cite{2013MNRAS.434..765K} approximating a black-hole silhouette could
be recovered from the light curve.

     
Gravitational microlensing of QSOs have been predicted as early as 1981 when \cite{1981ApJ...243..140G} suggested that 
``if haloes of galaxies were composed of stars with masses less than  0.1 $M_\odot$, then these stars acting as individual lenses would produce fluctuations of the order of 
unity in the intensities of the QSO images on time scales of 1 -14 years '' . 
What creates the magnification event is the relative and independent motion of the lens and source with respect to the observer.
Since the respective lens is surrounded by similar objects one would expect to observe during a long enough time interval
multiple microlensing events of the same source, the QSO. 
The sequential alignment of the source and observer with different lensing objects will result in an apparently random increase of the QSO light flux analogous to the scintillation events in a meter of radioactivity.\\


The Schwarzschild radius of the Sgr A* black hole, situated at 8~kpc from Earth \citep{1993ARA&A..31..345R} spans an angle of 10 microarcsec on the sky \citep{2008JPhCS.131a2055D}. If the quasars observed at $z=2$ would have similar linear sizes, the aparent size of the luminous part of the QSO would be many orders of magnitude below the 1 microarcsec level. Therefore the aparent size would be significantly smaller than the corresponding Einstein radius of a solar mass lens.
The magnitude differences between the Einstein angle and the aparrent size of the bright part of the QSO motivates the introduction in the first part of the paper of simplified models for     
calculating the lightcurves of QSO magnification events. The simplified models are introduced in the theory section of the present paper. The theory (II) section of the present article starts with an introduction to the basic microlensing theory in which we present the general microlensing equation followed by the concept of magnification. We underline that for the particular case of micro gravitational lensing,
the images are not resolved and thus the magnifications of each images contribute to a total magnification. 
Furthermore, the concept of critical curves and caustics are introduced. Afterwards we focus on a particular catastrophe, namely the fold. 
We choose to study events related to the previously mentioned singularity since the magnification events caused by the crossing of such boundaries are most probable. A quick inspection of figure \ref{fig:magnification_map} by the reader should motivate the previous statement. 
In continuation we introduce the commonly used result involving the magnification of a point-like source near a fold singularity. 
Namely that the magnification is approximately linear outside the caustic and decreases from infinity with the square root of the distance to the boundary when inside the caustic.  
In the last section of the theory (II) we present the general equations for estimating the flux received from an extended source near a fold. 
The only elements required to compute the flux as a function of time are the two dimensional brightness function of the object and the magnification of a point-like source. 
One of the core assumptions made when developing the simple models is that the Einstein angle is orders of magnitude greater than the apparent size of the source. 
Due to this assumption one can imagine the caustic as an infinite wall to be crossed by the source as presented in \ref{fig:infinite_fold}. 
The consequence of the limit is that the information regarding the profiles of the source along any direction parallel to the boundary value is reduced to the corresponding integral value. 
The effect allows the introduction of a one dimensional flux function, which is the two dimensional flux integrated along the axis parallel to the boundary. 
The one dimensional profile contains exhaustively all the information that can be extracted  from the lens generated light-curve \\


In the third section we introduce the three source profiles used in our models and simulations. We start with two commonly used and simple sources. Namely the gaussian brightness distribution and the constant intensity disk. In addition we use a geometric crescent-shaped source effectively the same as the one introduced by \citep{2013MNRAS.434..765K} with constant surface brightness. \\ The fourth section contains the results of our simplified models calculations, including the numerical equation for lightcurve calculations and the corresponding plots. 
In order to facilitate comparison between the lightcurves of the three distinct sources, we constrain the luminosity and half-light radius of all sources to have the same value. 
Furthermore, towards the end of the section, the microlensing light curves were generated for more complex images of black hole silhouettes. 
Namely the images of Sgr A* and M87 compiled in the paper \citep{2015MNRAS.446.1973R} and based on simulations presented in \citep{2009MNRAS.394L.126M} article were used as sources.     
       
We continue to the second part of the paper, where we have advanced the level of complexity of the amplification map. Using the Wambsganss gravitational lensing code \citep{1990LNP...360..186W} a realistic magnification map is generated. The numerical method, hierarchical tree structure and backwards raytracing, underlying the microlensing code is treated in section five. Aside from a basic review of the physical and numerical principles of the code, the description of its generalization from disk shaped source images to crescent ones can be found in the Microlensing code and magnification map as well. Furthermore, the mass distribution in the lens plane, chosen to produce the magnification map used in this analysis, is introduced and motivated.   

In section \ref{sec:fitting}, we carried out a likelihood analysis for the parametrisation of the different source shapes and study the degeneracies involved amongst them. To do so, we mocked the datasets corresponding to each source shape and contaminate them with different noise components. Finally we run MCMC to explore the parameter space of the source shape and some nuisance parameters. The motivation of this part is to explore the possibility if using a simple toy model is it possible to differentiate between symmetric and asymmetric sources based on maximum likelihood analysis. 


Finally, in the Discussion (VII) section, the main results of the current work and their implications are discussed. 
