\documentclass[usenatbib]{mn2e}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{multicol}

\title{Probing the internal structures of quasars using microlensing events}

\author[Tomozeiu et al]{Mihai Tomozeiu\thanks{mihai@physik.uzh.ch},$^{1,2}$ 
Irshad Mohammed,$^{1,2,3}$ 
Manuel Rabold,$^{1,2}$
Prasenjit Saha,$^{1,2}$  
\newauthor
and Joachim Wambsganss$^4$\\
$^1${Physik-Institut, University of Zurich, Winterthurerstrasse 190,
  8057 Zurich, Switzerland} \\
$^2${Institute for Computational Science, University of Zurich,
  Winterthurerstrasse 190, 8057 Zurich, Switzerland} \\
$^3${Theoretical Astrophysics Group, Fermi National Accelerator Laboratory, Batavia, IL 60510, USA}\\
$^4${Zentrum f\"ur Astronomie der Universit\"at Heidelberg,
  M\"onchhofstrasse 12--14, 69120 Heidelberg, Germany}
}

\begin{document}

\maketitle

\begin{abstract}

In quasars that have been lensed by galaxies, the point-like images
sometimes show sharp brightness variations (microlensing).  These
brightness changes are associated with the innermost region of the
quasar passing behind a complicated pattern of caustics due to the
stars in the lensing galaxy.  In this paper, we study whether the
universal properties of optical caustics could enable extraction of
shape information about the central engine of quasars.  We present a
toy model with a crescent-shaped source crossing a fold caustic.  The
silhouette of a black hole over an accretion disk tends to produce
roughly crescent sources.  When a crescent source crosses a fold
caustic, the resulting light curve is noticeably different from the
case of a disc or Gaussian source.  The crescent parameters, apart
from one degeneracy, can be recovered.
\end{abstract}


\begin{keywords}
Supermassive black holes, microlensing, quasars.
\end{keywords}


\input{intro}

\input{theory}

\input{numerics}

\input{discussion}


\bibliographystyle{mn2e}

\def\apj{ApJ}
\def\apjl{ApJL}
\def\aj{AJ}
\def\mnras{MNRAS}
\def\aap{A\&A}
\def\nat{nature}
\def\araa{ARAA}
\def\pasa{PASA}
\bibliography{heap}

\end{document}
